### 2015-11-08 ch02-qlogms/logMS_IMTC.tex
Figure ID cycle + some intro exp design

  \subsection{The system under consideration}
  We consider the transfer function models of generic linear time-invariant systems of arbitrary but finite orders $n_a\times n_b$:
  \begin{align}
    G\left( \Omega, \theta \right) = \frac{B\left( \Omega,\theta \right)}
                                          {A\left( \Omega,\theta \right)}
                                   = \frac{\sum\limits_{i=0}^{n_b-1} b_i \Omega^i}
                                          {\sum\limits_{i=0}^{n_a-1} a_i \Omega^i}
    \text{.} \label{eq:model}
  \end{align}

@@

  When designing an excitation signal, it is common only to specify a (large) frequency band
  by its boundary frequencies $f_{\min}$ and $f_{\max}$.
  For a given $\alpha$ it is easy to determine the number of excited lines
  within the frequency range of interest:
    \begin{equation}
      F = \floor{
                  \frac{\log{f_{\max}} - \log{f_{\min}}}
                       {\log{\alpha}}
                }
    \end{equation}
  where $\floor{\bullet}$ denotes rounding towards zero.
  In the Section \ref{sec:optimAlpha}, the choice of a suitable $\alpha$ is elaborated.

@@

  \begin{property}
    Each decade that is completely  within the range of excited frequencies $\set{f_1, \ldots, f_F}$ contains
   \begin{equation}
     F_{\decade} \isdef
     \floor{\frac{\log (10 f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} 10}
   \end{equation}
   excited frequency lines.
   I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
  \end{property}

   Obviously, the same argument can be held for any relative bandwidth (e.g. octave or even the $\wdB$ of a particular system).

>>>>

  \subsection{The system under consideration}
  We consider the transfer function models of generic \gls{LTI} systems of arbitrary but finite orders $n_a\times n_b$:
  \begin{align}
    G\left( \Omega, \theta \right) = \frac{B\left( \Omega,\theta \right)}
                                          {A\left( \Omega,\theta \right)}
                                   = \frac{\sum\limits_{i=0}^{n_b-1} b_i \Omega^i}
                                          {\sum\limits_{i=0}^{n_a-1} a_i \Omega^i}
    \text{.} \label{eq:model}
  \end{align}

@@

  When designing an excitation signal, it is common only to specify a (large) frequency band
  by its boundary frequencies $f_{\min}$ and $f_{\max}$.
  For a given $\alpha$ it is easy to determine the number of excited lines
  within the frequency range of interest:
    \begin{equation}
      F = \floor{
                  \frac{\log{f_{\max}} - \log{f_{\min}}}
                       {\log{\alpha}}
                }
    \label{eq:logms:F}
    \end{equation}
  where $\floor{\bullet}$ denotes rounding towards zero.
  In the Section \ref{sec:optimAlpha}, the choice of a suitable $\alpha$ is elaborated.

@@

  \begin{property}
   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
   \begin{equation}
     F_{B}(f) \isdef
     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} \kappa}
         \text{.}
   \end{equation}
   \end{property}
  \begin{example}
    For the frequency decade band $\decade(f) = \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
  \end{example}

   Obviously, the same argument can be held for any set of frequency bands with constant relative bandwidth (e.g. octave $\kappa = 2$).
   I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.

### 2015-11-08 config/glossaries.inc.tex
Figure ID cycle + some intro exp design

@@

\newsymbolglos{norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}
\newsymbolglos{norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
\newsymbolglos{norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}

\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
\newsymbolglos{lcm}{\lcm}{Least common multiple}
\newsymbolglos{cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{SetR}{\RealNumbers}{Set of the real numbers}
\newsymbolglos{SetZ}{\IntegerNumbers}{Set of integer numbers}
\newsymbolglos{SetC}{\ComplexNumbers}{Set of the complex numbers}
\newsymbolglos{SetN}{\NaturalNumbers}{Set of the natural numbers}
\newsymbolglos{w}{\omega}{Angular frequency (pulsation)}

\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a system}
\newsymbolglos{sys-damping}{\damping}{Relative damping of a system}
\newsymbolglos{sys-timeconst}{\tau}{Time constant of a system}

\newsymbolglos{matrix-eye}{\I_n}{ $n \times n$ identify matrix }

\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}

>>>>

\newsymbolglos{A-SetC}{\ComplexNumbers}{Set of the complex numbers}
\newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
\newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
\newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
\newsymbolglos{A-SetZ}{\IntegerNumbers}{Set of integer numbers}

@@

\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}

\newsymbolglos{lcm}{\lcm}{Least common multiple}

\newsymbolglos{matrix-eye}{\I_n}{ $n \times n$ identity matrix}

\newsymbolglos{norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
\newsymbolglos{norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}
\newsymbolglos{norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}

\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-ln}{\ln \placeholder}{Natural logarithm of \placeholder}
\newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when B is omitted, the decimal logarithm is implied)}
\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}

\newsymbolglos{sys-damping}{\damping}{Relative damping of a system}
\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a system}
\newsymbolglos{sys-timeconst}{\tau}{Time constant of a system}

\newsymbolglos{w}{\omega}{Angular frequency (pulsation)}
